\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-08 paper.tex
small fix

\begin{figure}[tb]
  \centering
  	\includegraphics[width=0.3\textwidth]{fig/example_motion.png}
  \caption{
    \captionstyle
  	Example possible motion using the double-integrator minimum time model between start state $(x_1, \dot{x_1}$ and goal state $(x_2, \dot{x_2}$ through some intermediate state $(x_i, \dot{x_i})$.
  	}
   	\label{fig:sample_dimt}
\end{figure}

@@

Following the example of recent work in path planning algorithms such as ~\ref{} (CHOMP?), we propose to solve the problem of efficiently sampling uniformly in the level set by using Monte Carlo sampling methods. Monte Carlo sampling methods have been used in the statics and machine learning fields to sample from intractable posteriors. Monte Carlo methods have the desirable property that they are guaranteed to sample the true posterior as the number of steps goes toward infinity.

>>>>

\begin{figure}[tb]
  \centering
  	\includegraphics[width=0.3\textwidth]{fig/example_motion.png}
  \caption{
    \captionstyle
  	Example possible motion using the double-integrator minimum time model between start state $(x_1, \dot{x_1})$ and goal state $(x_2, \dot{x_2})$ through some intermediate state $(x_i, \dot{x_i})$.
  	}
   	\label{fig:sample_dimt}
\end{figure}

@@

Following the example of recent work in path planning algorithms such as CHOMP~\cite{RZBS09}, we propose to solve the problem of efficiently sampling uniformly in the level set by using Monte Carlo sampling methods. Monte Carlo sampling methods have been used in the statics and machine learning fields to sample from intractable posteriors. Monte Carlo methods have the desirable property that they are guaranteed to sample the true posterior as the number of steps goes toward infinity.
